---
title: "Prepare a MSA spectrum from MCXRAY output"
author: "John Minter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Prepare a MSA spectrum from MCXRAY output}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Our objective is to convert to an .msa spectrum the output from a Monte
Carlo simulation using MCXRAY of the X-Ray EDS spectrum from 20 nm of
C on 50 nm of SiO~2~ on bulk Si at 3 kV. We'll copy this spectrum to
our **HOME** directory along with a .msa spectrum produced by a Monte
Carlo simulation performed using DTSA-II. This will permit us to compare
the two simulations.


## Load a spectrum

First we get our exemplar file from the data included with the R
package.

```{r}
inF <- system.file("extdata", "20nm-C-50nm-SiO2-Si-03kV.txt",
                    package = "rEDS")
inF
```

Then we create our MSA spectrum the `mcxrayToMsa` function.

```{r, message=FALSE}
library(rEDS)

ouNa <- "20nm-C-50nm-SiO2-Si-03kV.msa"

homDir   <- Sys.getenv('HOME')
homDir   <- gsub("\\\\", "/", homDir)
ouF      <- sprintf("%s/%s", homDir, ouNa)

mcxrayToMsa(inF, ouF, 3.0, 1.0, 100.0,
            '20nm-C-50nm-SiO2-Si-03kV', 'jrminter', TRUE)

print(ouF)
```

Now copy the DTSA file from the data included with the R package

```{r}
dtsaFN <- "20-nm-C-on-50-nm-SiO2-on-Si-at-3-kV-20000-Traj.msa"
inDF <- system.file("extdata", dtsaFN, package = "rEDS")
ouDtsaFN <- sprintf("%s/%s", homDir, dtsaFN)

print(ouDtsaFN)

file.copy(inDF, ouDtsaFN, TRUE, FALSE, TRUE, TRUE)
```

Now open and annotate the spectra using DTSA-II. You can export
publication quality output that may be 'tweaked' using gnuplot.


